### 2014-02-21 paper/retrofit.tex
minor
fix

We consider language of the form |(S, E, e, -->)|, where |S| is some
global state, |E| is an evaluation context, |e| is an expression in
the language and |-->| is the reduction relation on the state,
evaluation context and expression;
we say expression |e| in context |E| and state |S| reduces to
expression |e'| in context |E'| and state |S'| and write
|conf S (E[e]) --> conf S' (E'[e'])|.

@@

\begin{mathpar}
\inferrule[T-app]
{ } {| conf tS (intE ((\x.te) tv)) --> conf tS (intE ({tv/x} tv)) |}

\and
\inferrule[T-ifTrue]
{ } {| conf tS (intE (if true then te1 else te2)) --> conf tS (intE te1) |}

\and
\inferrule[T-ifFalse]
{ } {| conf tS (intE (if false then te1 else te2)) --> conf tS (intE te2) |}

\and
\inferrule[T-ref]
{| tS' = tS [ ta mapsto tv ] |} 
{| conf tS (intE (ref tv)) --> conf tS' (intE tv) |}
{| fresh ta |}

\and
\inferrule[T-deref]
{| (ta, tv) member tS |}
{| conf tS (intE (!ta)) --> conf tS (intE tv) |}

\and
\inferrule[T-ass]
{| tS' = tS [ ta mapsto tv ] |} 
{| conf tS (intE (ta := tv)) --> conf tS' (intE tv) |}
\end{mathpar}

@@

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
       |  fork ie | send ie ie ie | ix1, ix2 <= recv. ie ie |  IT te
iE   ::=  iE lop ie | iv lop iE | setLabel iE | fork iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  ix1, ix2 <= recv. ie ie |  IT tE
Q    ::=  nil | (il, id, ie) :: Q

@@

\begin{mathpar}
\inferrule[I-getLabel]
{ }
{|
iconf iS (lconf id il tS (iniE (getLabel)), ldots)
-->
iconf iS (lconf id il tS (iniE il), ldots)
|}
\and
\inferrule[I-setLabel]
{ |il canFlowTo il'| }
{|
iconf iS (lconf id il tS (iniE (setLabel il')), ldots)
-->
iconf iS (lconf id il' tS (iniE unit), ldots)
|}
\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = q(tS)|
}
{|
iconf iS (lconf id il tS (iniE (fork ie)), ldots)
-->
iconf iS' (lconf id il tS (iniE id'), ldots, lconf id' il tS' (TI ie))
|}
{|fresh (id')|}
\and
\inferrule[I-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ id' mapsto (il', id,  ie) :: Q ]|
}
{|
iconf iS (lconf id il tS (iniE (send id' il' ie))), ldots)
-->
iconf iS' (lconf id il tS (iniE unit), ldots)
|}
\and
\inferrule[I-recv]
{
| filter il (iS(id)) = (il', id', ie') :: Q'|\\
| iS' = iS[id mapsto Q']|
}
{|
iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2))), ldots)
-->
iconf iS' (lconf id il tS (iniE ({ie'/ix1,id'/ix2} ie1)), ldots)
|}
\and
\inferrule[I-noRecv]
{
| filter il (iS(id)) = nil|\\
| iS' = iS[id mapsto nil]|
}
{|
iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2))), ldots)
-->
iconf iS' (lconf id il tS (iniE ie2), ldots)
|}
\and
\inferrule[I-bool]
{ |b member {true, false}|  } {| iniE (IT b) --> iniE b |}
\and
\inferrule[I-border]
{ } {| iniE (IT (TI (ie))) --> iniE ie |}
\and
\inferrule[T-bool]
{ |b member {true, false}| } {| intE (TI b) --> intE b |}
\and
\inferrule[T-border]
{ } {| intE (TI (IT (te))) --> intE te |}
\end{mathpar}

\caption{IFC language}
\label{fig:ml}
\end{figure}

@@

>>>>

We consider language of the form |(S, E, e, ->)|, where |S| is some
global state, |E| is an evaluation context, |e| is an expression in
the language and |->| is the reduction relation on the state,
evaluation context and expression;
we say expression |e| in context |E| and state |S| reduces to
expression |e'| in context |E'| and state |S'| and write
|conf S (E[e]) -> conf S' (E'[e'])|.
$|->| : (|S| \times |E| \times |e|) \rightharpoonup (|S| \times |E| \times |e|)$

@@

\begin{mathpar}
\and
\inferrule[T-pure]
{| te ~> te'|}
{| conf tS te -> conf tS te' |}

\and
\inferrule[T-app]
{ } {| intE ((\x.te) tv) ~> intE ({tv/x} tv) |}

\and
\inferrule[T-ifTrue]
{ } {| intE (if true then te1 else te2)  ~> intE te1 |}

\and
\inferrule[T-ifFalse]
{ } {| intE (if false then te1 else te2) ~> intE te2 |}

\and
\inferrule[T-ref]
{| tS' = tS [ ta mapsto tv ] | } 
{| conf tS (intE (ref tv)) -> conf tS' (intE ta) |}
{| fresh (ta) |}

\and
\inferrule[T-deref]
{| tv = tS(ta) |}
{| conf tS (intE (!ta)) -> conf tS (intE tv) |}

\and
\inferrule[T-ass]
{| tS' = tS [ ta mapsto tv ] |} 
{| conf tS (intE (ta := tv)) -> conf tS' (intE tv) |}
\end{mathpar}

@@

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
       |  fork ie | send ie ie ie | ix1, ix2 <= recv. ie ie |  IT te
iE   ::=  iE lop ie | iv lop iE | setLabel iE | fork iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  ix1, ix2 <= recv. ie ie |  IT tE
io   ::=  (il, id ie)
Q    ::=  nil | io :: Q

@@

\begin{mathpar}
\inferrule[I-step]
{|
  conf tS (intE te) -> conf tS (intE te')
|}
{|
iconf iS (lconf id il tS (IT (intE te)), ldots)
.->
iconf iS (lconf id il tS' (IT (intE te')), ldots)
|}

\and
\inferrule[I-getLabel]
{ }
{|
iconf iS (lconf id il tS (iniE (getLabel)), ldots)
.->
iconf iS (lconf id il tS (iniE il), ldots)
|}

\and
\inferrule[I-setLabel]
{ |il canFlowTo il'| }
{|
iconf iS (lconf id il tS (iniE (setLabel il')), ldots)
.->
iconf iS (lconf id il' tS (iniE unit), ldots)
|}

\and
\inferrule[I-fork]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = q(tS)|\\
|fresh (id')|
}
{|
iconf iS (lconf id il tS (iniE (fork ie)), ldots)
.->
iconf iS' (lconf id il tS (iniE id'), ldots, lconf id' il tS' (TI ie))
|}
%{|fresh (id')|}

\and
\inferrule[I-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ id' mapsto (il', id,  ie) :: Q ]|
}
{|
iconf iS (lconf id il tS (iniE (send id' il' ie))), ldots)
.->
iconf iS' (lconf id il tS (iniE unit), ldots)
|}

\and
\inferrule[I-recv]
{
| filter il (iS(id)) = io1 :: cdots :: iok :: (il', id', ie')|\\
| iS' = iS[id mapsto io1 :: cdots :: iok]|\\
| ie1'' = {ie'/ix1,id'/ix2} ie1|
}
{|
iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2)), ldots)
.->
iconf iS' (lconf id il tS (iniE ie1''), ldots)
|}

\and
\inferrule[I-noRecv]
{
| filter il (iS(id)) = nil|\\
| iS' = iS[id mapsto nil]|
}
{|
iconf iS (lconf id il tS (iniE (ix1, ix2 <= recv. ie1 ie2)), ldots)
.->
iconf iS' (lconf id il tS (iniE ie2), ldots)
|}

\inferrule[I-pure]
{| ie .~> ie'|}
{|
  iconf iS (lconf id il tS ie)
.->
  iconf iS (lconf id il tS ie)
|}

\and
\inferrule[I-labelOp]
{ |denot (il lop il') = iv|}
{ |iniE (il lop il') .~> iniE iv| }

\and
\inferrule[I-border]
{ } {| iniE (IT (TI (ie))) .~> iniE ie |}

\and
\inferrule[T-border]
{ } {| intE (TI (IT (te))) ~> intE te |}
\end{mathpar}
\caption{IFC language nad general embedding.}
\label{fig:ml}
\end{figure}

@@

In the case of extending
\begin{mathpar}
\inferrule[I-bool]
{ |b member {true, false}|  } {| iniE (IT b) -> iniE b |}
\and
\inferrule[T-bool]
{ |b member {true, false}| } {| intE (TI b) -> intE b |}
\end{mathpar}
